Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-24 awipev-CO2.Rmd
modif on seafet graph with depth group

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
library(robfilter)
library(seacarb)
library(gridExtra)
library(reshape2)
library(lubridate)
library(lmtest)
library(grid)
library(viridis)
library(dygraphs)
require("knitr")
library("lmodel2")
library(captioner)
library(xts)
library(seismicRoll)
library(scales)
knitr::opts_chunk$set(echo = TRUE)

@@

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered)
```

@@

@@

p_sal_fb_sal_insitu<-  ggplot(d_all,aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("Sal in situ vs Sal FB","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="Salinity insitu", y="Salinity FB ", color = "Months")  +theme_bw()
print(p_sal_fb_sal_insitu)

@@

- 1 SBE45 inside the Ferrybox (temp_fb)
- 5 CTD > 8 meters depth (sal_insitu_ctd)
- 5 fixed at 11 meters depth (sal_insitu_11m)

@@

### **T seaFET / T mix **

@@

fit <- lmodel2(data = d_all,  T_seaF ~ temp_mix , nperm = 99)

```{r Temp comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# seaF outliers (T - volt int - volt ext) to remove from 2017-12-10 to 2017-12-14
d_all <- d_all %>%
  dplyr::mutate(T_seaF = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, T_seaF),
                voltINT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltINT), 
                voltEXT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltEXT))

fit <- lmodel2(data = d_all,  T_seaF ~ temp_mix , nperm = 99)

pTseaf_Tinsi<-  ggplot(d_all,aes(x=temp_mix, y= T_seaF, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = T_seaF, y = T_seaF), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T seaF vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T insi", y="T seaF ", color = "Months")  +theme_bw()
print(pTseaf_Tinsi)

d_all$diff_T_seaF_insitu <- d_all$T_seaF - d_all$temp_mix
mean_diff_T_seaF_insitu <- round(mean(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)
sd_diff_T_seaF_insitu <- round(sd(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)

The mean difference between T seaFET and in situ is: `r mean_diff_T_seaF_insitu` ± `r sd_diff_T_seaF_insitu`°C.

### **T Ferrybox / T mix **

fit <- lmodel2(data = d_all,  temp_fb ~ temp_mix , nperm = 99)

@@

fit <- lmodel2(data = d_all,  temp_fb ~ temp_mix , nperm = 99)

pTfb_Tinsi<-  ggplot(d_all,aes(x=temp_mix, y= temp_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = temp_fb, y = temp_fb), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T FB vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
print(pTfb_Tinsi)

d_all$diff_T_fb_insitu <- d_all$T_seaF - d_all$temp_mix
mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
```

@@

d_all$diff_T_fb_insitu <- d_all$T_seaF - d_all$temp_insitu_ctd
mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
```

@@

pH is measured continuously by an autonomous seaFET pH sensor. Because of issue, measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17. pH calibration is based on monthly discrete samples that are analysed with spectrophotometric method in Villefranche by Samir Alliouane. When it is not possible to sample at the vicinity of the sensor for practice reasons (in winter), sampling is done in the harbour and is not taken in consideration for calibration for spatial reasons.

@@

mean_TseaF_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all%>%
  dplyr::mutate(temp_mix = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_mix))

@@

mean_TseaF_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all%>%
  dplyr::mutate(temp_mix = ifelse(datetime == "2019-09-13 13:00:00" , mean_TseaF_4h, temp_mix))

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_insitu,
                          calT = d_all$temp_mix, calSal = d_all$sal_mix )
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE, warning=FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_mix, calSal = d_all$sal_mix_interp)

@@

seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_insitu,pHint_tot_sf, pH_s_sf_no_calb)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
    dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_s_seafet_temp_insitu", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%

@@

  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[22], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_insitu, T_seaF, temp_fb, temp_insitu, sal)
# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
#   #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
#    # dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
#     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
#   dySeries("temp_insitu", label = "temp_insitu", color ="red", strokeWidth=0, pointSize=2) %>%
# dySeries("temp_fb", label = "temp_fb", color ="blue", strokeWidth=0, pointSize=2) %>%
#  # dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
#    # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
#  #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
#   #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
#   #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
#    # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
#   dyLegend(show = "auto")   %>%
#   #dyAxis( "y2",valueRange = c(-3, 36))%>%
#   dyAxis( "y",valueRange = c(-3, 9))%>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
#   dyRangeSelector(height = 30, dateWindow= NULL)
# # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

>>>>

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
library(robfilter)
library(seacarb)
library(gridExtra)
library(reshape2)
library(lubridate)
library(lmtest)
library(grid)
library(viridis)
library(dygraphs)
require("knitr")
library("lmodel2")
library(captioner)
library(xts)
library(seismicRoll)
library(scales)
library(plotly)
library(htmlwidgets)
knitr::opts_chunk$set(echo = TRUE)

@@

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered, temp_sf=T_seaF)
```

@@

```{r Depth filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
#Make groups

d_all <- d_all%>%
  dplyr::mutate(depth = ifelse(pressure_insitu_ctd_filtered <=2, "1 m", 
                        ifelse(pressure_insitu_ctd_filtered >2 & pressure_insitu_ctd_filtered <=4, "3 m", 
                        ifelse(pressure_insitu_ctd_filtered >4 & pressure_insitu_ctd_filtered <=6, "5 m",
                        ifelse(pressure_insitu_ctd_filtered >6 & pressure_insitu_ctd_filtered <=8, "7 m",
                        ifelse(pressure_insitu_ctd_filtered >8, "9 m",NA))))))
```

@@

# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,sal_fb,sal_insitu_ctd)
# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
#   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
#   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) 
#

p_sal_fb_sal_insitu<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
  coord_fixed(ratio = 1 )+
   scale_colour_discrete(guide="none") +
  labs( x="Salinity CTD > 8 m", y="Salinity FB ", color = "Months") +theme_bw()
print(p_sal_fb_sal_insitu)

@@

- 1 SBE45 inside the Ferrybox (temp_fb)
- 5 CTD > 8 meters depth (temp_insitu_ctd)
- 1 fixed at 11 meters depth (temp_insitu_11m)

@@

### **T Ferrybox / T insitu 11 m **

@@

fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)

@@

fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)

p<-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = temp_fb, y = temp_fb), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T FB vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
print(p)

d_all$diff_T_fb_insitu <- d_all$temp_sf - d_all$temp_insitu_11m
mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
```

@@

d_all$diff_T_fb_insitu <- d_all$temp_sf - d_all$temp_insitu_ctd
mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
```

@@

pH is measured continuously by an autonomous seaFET pH sensor. Because of issue, measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17. *Note that pH sensor is mounted on a profiling structure. Here, only seaFET data recorded with a depth > 8 m are taken in consideration.* pH calibration is based on monthly discrete samples that are analysed with spectrophotometric method in Villefranche by Samir Alliouane. When it is not possible to sample at the vicinity of the sensor for practice reasons (in winter), sampling is done in the harbour and is not taken in consideration for calibration for spatial reasons.

@@

mean_TseaF_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(temp_sf, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all%>%
  dplyr::mutate(temp_mix = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_mix))

@@

mean_TseaF_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
  dplyr::summarise( mean(temp_sf, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all%>%
  dplyr::mutate(temp_mix = ifelse(datetime == "2019-09-13 13:00:00" , mean_TseaF_4h, temp_mix))

@@

d_all <-  d_all%>%
  dplyr::mutate(voltINT_sup8m = ifelse(pressure_insitu_ctd_filtered >=8,voltINT, NA),
                voltEXT_sup8m = ifelse(pressure_insitu_ctd_filtered >=8,voltEXT, NA), 
                pH_s_seafet_temp_insitu_sup8m = ifelse(pressure_insitu_ctd_filtered >=8,pH_s_seafet_temp_insitu, NA) )
####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT_sup8m, calEext = d_all$voltEXT_sup8m, calpH = d_all$pH_s_seafet_temp_insitu_sup8m,
                          calT = d_all$temp_mix, calSal = d_all$sal_mix )
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE, warning=FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib <- sf_calc(calEint = d_all$voltINT_sup8m, calEext = d_all$voltEXT_sup8m, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_mix, calSal = d_all$sal_mix_interp)

@@

seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_insitu,pHint_tot_sf, pH_s_sf_no_calb, pressure_insitu_ctd_filtered)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  dySeries("pressure_insitu_ctd_filtered", axis="y2",label = "Depth", color ="pink", strokeWidth=0, pointSize=2) %>%
  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
    dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_s_seafet_temp_insitu", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%

@@

  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  # dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  # dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  # dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
  # dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
  # dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
  #  dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
  #  dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
  #  dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
  # dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
  # dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
  #  dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
  #  dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

p <- ggplot(d_all%>%filter(datetime >= ("2017-07-30")),aes(x=datetime, y= phINT_filtered, label = depth))+
  geom_line( aes(color=factor(depth)))

p_py <- ggplotly(p,dynamicTicks = TRUE)
filename.html <- paste0("/figures/p_py.html")
saveWidget(p_py, filename.html, selfcontained = T, libdir = "lib")

getwd()

seafet_depth_xts <- dplyr::select(d_all, datetime, phINT_filtered, depth)
seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
dygraph(seafet_depth_xts, group = "depth", main="pH seaFET RAW (in situ)", ylab="pHT") %>%
  dySeries("phINT_filtered", axis="y2",label = "pH RAW", color ="green", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%
  #dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
  #dyGroup(depth, drawPoints = TRUE, color = "green")%>%
  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_insitu, temp_sf, temp_fb, temp_insitu, sal)
# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
#   #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
#    # dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
#     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
#   dySeries("temp_insitu", label = "temp_insitu", color ="red", strokeWidth=0, pointSize=2) %>%
# dySeries("temp_fb", label = "temp_fb", color ="blue", strokeWidth=0, pointSize=2) %>%
#  # dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
#    # dySeries("temp_sf", label = "temp_sf", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
#  #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
#   #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
#   #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
#    # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
#   dyLegend(show = "auto")   %>%
#   #dyAxis( "y2",valueRange = c(-3, 36))%>%
#   dyAxis( "y",valueRange = c(-3, 9))%>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
#   dyRangeSelector(height = 30, dateWindow= NULL)
# # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
